---
title: "main"
author: "group 6"
date: "4/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries & Reading In Data
```{r}
source("../lib/functions.R")
setwd("~/Documents/GitHub/project-3-algorithms-group_6/doc")
```

### MS Data
```{r reading ms data, eval = FALSE}

# Load the data
MS_train <- read.csv("../data/MS_sample/data_train.csv", as.is = TRUE, header = TRUE)
MS_train <- MS_train[, 2:4]

MS_test <- read.csv("../data/MS_sample/data_test.csv", as.is = TRUE, header = TRUE)
MS_test <- MS_test[, 2:4]


# Transform from narrow to wide, i.e. user-item matrix 
# using MS_data_transform function & save to Rdata and csvs. 

MS_train <- MS_data_transform(MS_train)
save(MS_train, file = "MS_UI.RData")
write.csv(MS_train, "ms_train.csv")

MS_test <- MS_data_transform(MS_test)
save(MS_test, file = "MS_UI_test.RData")
write.csv(MS_test, "ms_test.csv")
```

### Movie Data
```{r reading movie data, eval = FALSE}
# Load the data from csv and write to Rdata
movie_train <- read.csv("./Proj3_Data/eachmovie_sample/data_train.csv", as.is = TRUE, header = TRUE)
movie_train <- movie_train[, 2:4]
movie_test <- read.csv("./Proj3_Data/eachmovie_sample/data_test.csv", as.is = TRUE, header = TRUE)
movie_test <- movie_test[, 2:4]

users  <- sort(unique(movie_train$User))
movies <- sort(unique(movie_train$Movie))

# initialize UI matrix
UI            <- matrix(NA, nrow = length(users), ncol = length(movies))
row.names(UI) <- users
colnames(UI)  <- movies

# We consider just user 1, finding user 1's movies and ratings
movies  <- movie_train$Movie[movie_train$User == users[1]]
ratings <- movie_train$Score[movie_train$User == users[1]]

ord     <- order(movies)
movies  <- movies[ord]
ratings <- ratings[ord]

system.time(UI[1, colnames(UI) %in% movies] <- ratings)

total_ratings <- rowSums(movie_UI, na.rm = TRUE)

# Compute the full matrix
# save to Rdata and csvs 
movie_train <- movie_data_transform(movie_train)
save(movie_train, file = "movie_train.RData")
write.csv(movie_train, "../data/movie_train.csv")

movie_test <- movie_data_transform(movie_test)
save(movie_test, file = "movie_test.RData")
write.csv(movie_test, "../data/movie_test.csv")
```

### Loading Data
```{r load data}
# load training and testing Rdata sets
# even though they are named nicely here, we stil refer to them as movie_UI etc. below. They are loading with those names, strangely. 
load("../data/movie_train.RData")
load("../data/movie_test.RData")
load("../data/MS_train.RData")
load("../data/MS_test.RData")
```

# Models 
## Memory-based Models 
### Pearson Correlation
```{r}
weight_pearson_MS_train <- calc_weight(MS_UI, method = 'pearson')
save(weight_pearson_MS_train, file = 'weight_pearson_MS_train.RData')

weight_pearson_movie_train <- calc_weight(movie_UI, method = 'pearson')
save(weight_pearson_movie_train, file = 'weight_pearson_movie_train.RData')
```
### Spearman Correlation
```{r}
weight_spearman_MS_train <- calc_weight(MS_UI, method = 'spearman')
save(weight_spearman_MS_train, file = 'weight_spearman_MS_train.RData')

weight_spearman_movie_train <- calc_weight(movie_UI, method = 'spearman')
save(weight_spearman_movie_train, file = 'weight_spearman_movie_train.RData')
```
### Cosine 
```{r}
weight_cosine_MS_train <- calc_weight(MS_UI, method = 'cosine')
save(weight_cosine_MS_train, file = 'weight_cosine_MS_train.RData')

weight_cosine_movie_train <- calc_weight(movie_UI, method = 'cosine')
save(weight_cosine_movie_train, file = 'weight_cosine_movie_train.RData')
```
### Entropy 
```{r}
weight_entropy_MS_train <- calc_weight(MS_UI, method = 'entropy')
save(weight_entropy_MS_train, file = 'weight_entropy_MS_train.RData')

weight_entropy_movie_train <- calc_weight(movie_UI, method = 'entropy')
save(weight_entropy_movie_train, file = 'weight_entropy_movie_train.RData')
```

### Mean Squared Difference
```{r}
weight_msd_MS_train <- calc_weight(MS_UI, method = 'msd')
save(weight_msd_MS_train, file = 'weight_msd_MS_train.RData')

weight_msd_movie_train <- calc_weight(movie_UI, method = 'msd')
save(weight_msd_movie_train, file = 'weight_msd_movie_train.RData')
```

## EM Algorithm
The EM algorithm can be found in the python jupyter notebook in the docs folder.

# Predictions
## Memory Based Algorithm
#### Load Similarity Weights
```{r}
# MS weight data are in GitHub repo, but movie weight data are too large to be uploaded to GitHub, so we uploaded them to GoogleDrive. 
# The Google Drive Link is: https://drive.google.com/open?id=1EMPXV5k9NDRp8rNTJtxVmImtkYaH72Pr
load("../output/weight_pearson_MS_train.RData")
load("../output/weight_pearson_movie_train.RData")
load("../output/weight_spearman_MS_train.RData")
load("../output/weight_spearman_movie_train.RData")
load("../output/weight_cosine_MS_train.RData")
load("../output/weight_cosine_movie_train.RData")
load("../output/weight_entropy_MS_train.RData")
load("../output/weight_entropy_movie_train.RData")
load("../output/weight_msd_MS_train.RData")
load("../output/weight_msd_movie_train.Rdata")
load("../output/weight_cosine_MS_train.RData")
```

### Original Prediction
#### With Pearson 
```{r web predict}
# Calculate predictions for MS
MS_pred_pearson <- pred_matrix(MS_UI, weight_pearson_MS_train)
save(MS_pred_pearson, file = "../output/MS_pred_pearson.RData")

movie_pred_pearson <- pred_matrix(movie_UI, weight_pearson_movie_train)
save(movie_pred_pearson, file = "../output/movie_pred_pearson.RData")
```
#### With Spearman 
```{r web predict}
# Calculate predictions for MS
MS_pred_spearman <- pred_matrix(MS_UI, weight_spearman_MS_train)
save(MS_pred_spearman, file = "../output/MS_pred_spearman.RData")

movie_pred_spearman <- pred_matrix(movie_UI, weight_spearman_movie_train)
save(movie_pred_spearman, file = "../output/movie_pred_spearman.RData")
```
#### With Cosine 
```{r web predict}
# Calculate predictions for MS
MS_pred_cosine <- pred_matrix(MS_UI, weight_cosine_MS_train)
save(MS_pred_cosine, file = "../output/MS_pred_cosine.RData.RData")

movie_pred_cosine <- pred_matrix(movie_UI, weight_cosine_movie_train)
save(movie_pred_cosine, file = "../output/movie_pred_cosine.RData")
```
#### With Mean-square Difference 
```{r web predict}
# Calculate predictions for MS
MS_pred_msd <- pred_matrix(MS_UI, weight_msd_MS_train)
save(MS_pred_msd, file = "../output/MS_pred_msd.RData")

movie_pred_msd <- pred_matrix(movie_UI, weight_msd_movie_train)
save(movie_pred_msd, file = "../output/movie_pred_msd.RData")
```
#### With Entropy 
```{r web predict}
# Calculate predictions for MS
MS_pred_entropy <- pred_matrix(MS_UI, weight_entropy_MS_train)
save(MS_pred_entropy, file = "../output/MS_pred_entropy.RData")

movie_pred_entropy <- pred_matrix(movie_UI, weight_entropy_movie_train)
save(movie_pred_entropy, file = "../output/movie_pred_entropy.RData")
```

### Z-Score Prediction
#### With Pearson
```{r web predict}
# Calculate predictions for MS
MS_pred_pearson <- pred_z_score_matrix(MS_UI, weight_pearson_MS_train)
save(MS_pred_pearson, file = "../output/MS_pred_pearson.RData")

movie_pred_pearson <- pred_z_score_matrix(movie_UI, weight_pearson_movie_train)
save(movie_pred_pearson, file = "../output/movie_pred_pearson.RData")
```
#### With Spearman 
```{r web predict}
# Calculate predictions for MS
MS_pred_spearman <- pred_z_score_matrix(MS_UI, weight_spearman_MS_train)
save(MS_pred_spearman, file = "../output/MS_pred_spearman.RData")

movie_pred_spearman <- pred_z_score_matrix(movie_UI, weight_spearman_movie_train)
save(movie_pred_spearman, file = "../output/movie_pred_spearman.RData")
```
#### With Cosine 
```{r web predict}
# Calculate predictions for MS
MS_pred_cosine <- pred_z_score_matrix(MS_UI, weight_cosine_MS_train)
save(MS_pred_cosine, file = "../output/MS_pred_cosine.RData.RData")

movie_pred_cosine <- pred_z_score_matrix(movie_UI, weight_cosine_movie_train)
save(movie_pred_cosine, file = "../output/movie_pred_cosine.RData")
```
#### With Mean-square Difference 
```{r web predict}
# Calculate predictions for MS
MS_pred_msd_zscore <- pred_z_score_matrix(MS_UI, weight_msd_MS_train)
save(MS_pred_msd_zscore, file = "../output/MS_pred_msd_zscore.RData")

movie_pred_msd_zscore <- pred_z_score_matrix(movie_UI, weight_msd_movie_train)
save(movie_pred_msd_zscore, file = "../output/movie_pred_msd_zscore.RData")
```
#### With Entropy 
```{r web predict}
# Calculate predictions for MS
MS_pred_entropy_zscore <- pred_z_score_matrix(MS_UI, weight_entropy_MS_train)
save(MS_pred_entropy_zscore, file = "../output/MS_pred_entropy_zscore.RData")

movie_pred_entropy_zscore <- pred_z_score_matrix(movie_UI, weight_entropy_movie_train)
save(movie_pred_entropy_zscore, file = "../output/movie_pred_entropy_zscore
     .RData")
```

<<<<<<< HEAD
=======
## EM Algorithm
```{r}
# load gamma
if(!require('RcppCNPy')){
  install.packages('RcppCNPy')
}

gamma0 <- npyLoad("../output/10gammas/gamma0.npy")
gamma1 <- npyLoad("../output/10gammas/gamma1.npy")
gamma2 <- npyLoad("../output/10gammas/gamma2.npy")
gamma3 <- npyLoad("../output/10gammas/gamma3.npy")
gamma4 <- npyLoad("../output/10gammas/gamma4.npy")
gamma5 <- npyLoad("../output/10gammas/gamma5.npy")
gamma6 <- npyLoad("../output/10gammas/gamma6.npy")
gamma7 <- npyLoad("../output/10gammas/gamma7.npy")
gamma8 <- npyLoad("../output/10gammas/gamma8.npy")
gamma9 <- npyLoad("../output/10gammas/gamma9.npy")
gamma <- array(0, dim = c(1619, 6, 10))
gamma[,,1] <- gamma0
gamma[,,2] <- gamma1
gamma[,,3] <- gamma2
gamma[,,4] <- gamma3
gamma[,,5] <- gamma4
gamma[,,6] <- gamma5
gamma[,,7] <- gamma6
gamma[,,8] <- gamma7
gamma[,,9] <- gamma8
gamma[,,10] <- gamma9

#load mu
mu <- npyLoad("../output/mu.npy")

# movie data
em_pred(movie_UI, gamma, mu, cl = 10, rng)

notNAs <- which(!is.na(movie_UI_test), TRUE)
load("../data/cluster_prediction.RData")


# calculate MAE 
mae <- 0
for (i in nrow(notNAs)){
    mae <- mae + sum(abs(preds[notNAs[i,1], notNAs[i,2]] - movie_UI_test[notNAs[i,1], notNAs[i,2]]))/nrow(notNAs)
  
}

## testing below
# nitems <- dim(movie_UI)[2]
# nusers <- dim(movie_UI)[1]
# 
# gamma <- array(1/6, dim = c(6, nitems, 12))
# sft <- matrix(0, nrow = nusers, ncol = 12)
# sft[ ,6] <- rep(1, nusers)
# rng <- 1:6

#ms dataset 


```
>>>>>>> 9a2aeaa271b5bcb4b4238e216923e035689906da

## Evaluation
### Load prediction data
```{r}
# Again, MS prediction data are in GitHub repo, but movie prediction data are in Google Drive. 
# The Google Drive Link is: https://drive.google.com/open?id=1EMPXV5k9NDRp8rNTJtxVmImtkYaH72Pr
load("../output/movie_pred_entropy_zscore.RData")
load("../output/MS_pred_entropy_zscore.RData")
load("../output/movie_pred_msd_zscore.RData")
load("../output/MS_pred_msd_zscore.RData")
load("../output/movie_pred_cosine_zscore.RData")
load("../output/MS_pred_cosine_zscore.RData")
load("../output/movie_pred_spearman_zscore.RData")
load("../output/MS_pred_spearman_zscore.RData")
load("../output/movie_pred_pearson_zscore.RData")
load("../output/MS_pred_pearson_zscore.RData")
load("../output/movie_pred_entropy.RData")
load("../output/MS_pred_entropy.RData")
load("../output/movie_pred_msd.RData")
load("../output/MS_pred_msd.RData")
load("../output/movie_pred_cosine.RData")
load("../output/MS_pred_cosine.RData")
load("../output/movie_pred_spearman.RData")
load("../output/MS_pred_spearman.RData")
load("../output/movie_pred_pearson.RData")
load("../output/MS_pred_pearson.RData")
```
### Original Memory-based Model
#### Pearson Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_pearson
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_pearson = rank_score(MS_test, MS_pred)
rank_score_pearson

# MAE for Movie
movie_pred <- movie_pred_pearson
movie_pred <- movie_pred[rownames(movie_UI_test),colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
#### Spearman Correlation
```{r}
# Rank of Score for Web
MS_pred<-MS_pred_spearman
MS_pred<-MS_pred[rownames(MS_test),colnames(MS_test)]
rank_score_spearman = rank_score(MS_test,MS_pred)
rank_score_spearman

# MAE for Movie
movie_pred <- movie_pred_spearman
movie_pred <- movie_pred[rownames(movie_UI_test),colnames(movie_UI_test)]
mae(movie_UI_test,movie_pred)
```
#### Cosine Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_cosine
MS_pred <- MS_pred[rownames(MS_test),colnames(MS_test)]
rank_score_cosine = rank_score(MS_test,MS_pred)
rank_score_cosine

# MAE for Movie
movie_pred <- movie_pred_cosine
movie_pred <- movie_pred[rownames(movie_UI_test),colnames(movie_UI_test)]
mae(movie_UI_test,movie_pred)
```
#### Mean-square Difference Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_msd
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_msd = rank_score(MS_test, MS_pred)
rank_score_msd

# MAE for Movie
movie_pred <- movie_pred_msd
movie_pred <- movie_pred[rownames(movie_UI_test), colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
#### Entropy Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_entropy
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_entropy = rank_score(MS_test, MS_pred)
rank_score_entropy

# MAE for Movie
movie_pred <- movie_pred_entropy
movie_pred <- movie_pred[rownames(movie_UI_test), colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
### Z-score Memory-based Model
#### Pearson Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_pearson_zscore
MS_pred <- MS_pred[rownames(MS_test),colnames(MS_test)]
rank_score_pearson_zscore = rank_score(MS_test,MS_pred)
rank_score_pearson_zscore

# MAE for Movie
movie_pred <- movie_pred_pearson_zscore
movie_pred <- movie_pred[rownames(movie_UI_test),colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
#### Spearman Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_spearman_zscore
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_spearman_zscore = rank_score(MS_test,MS_pred)
rank_score_spearman_zscore

# MAE for Movie
movie_pred <- movie_pred_spearman_z_score
movie_pred <- movie_pred[rownames(movie_UI_test),colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
#### Cosine Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_cosine_zscore
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_cosine_zscore = rank_score(MS_test,MS_pred)
rank_score_cosine_zscore

# MAE for Movie
movie_pred <- movie_pred_cosine_z_score
movie_pred <- movie_pred[rownames(movie_UI_test), colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
#### Mean-square Difference Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_msd_zscore
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_msd_zscore = rank_score(MS_test, MS_pred)
rank_score_msd_zscore

# MAE for Movie
movie_pred <- movie_pred_msd_zscore
movie_pred <- movie_pred[rownames(movie_UI_test), colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```
#### Entropy Correlation
```{r}
# Rank of Score for Web
MS_pred <- MS_pred_entropy_zscore
MS_pred <- MS_pred[rownames(MS_test), colnames(MS_test)]
rank_score_entropy_zscore = rank_score(MS_test, MS_pred)
rank_score_entropy_zscore

# MAE for Movie
movie_pred <- movie_pred_entropy_zscore
movie_pred <- movie_pred[rownames(movie_UI_test), colnames(movie_UI_test)]
mae(movie_UI_test, movie_pred)
```

